---
title: "Finansteori (SFB30820)"
subtitle: "Beregninger"
author: "Jørn I.Halvorsen"
date: "2021/08/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    includes:
      in_header: "mathjax-equation-numbers.html"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
#output: 
#  html_notebook:
#  toc: false
---

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
#xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
```

```{r eval=FALSE, include=FALSE}
Sys.which('decktape')
#xaringan::decktape("presentations.html", output="abc.pdf")
xaringan::inf_mr("tavlefil.Rmd")
```

# Kapitalmarkedslinja

\begin{equation}
E(r_p)=wr_f+(1-w)E(r_m)
\end{equation}

\begin{equation}
Var(r_p)=(1-w)^2Var(r_m)
\end{equation}

\begin{equation}
\frac{Std(r_p)}{Std(r_m)
}=(1-w) 
\end{equation}

\begin{equation}
E(r_p)=wr_f+(1-w)E(r_m) + (r_f - r_f) \\
E(r_p)=r_f+(1-w)(E(r_m) - rf) \\
\end{equation}

\begin{equation}
E(r_p)=r_f+\frac{Std(r_p)}{Std(r_m)}(E(r_m) - rf) \\
\end{equation}

---

# Enkeltprosjekt


\begin{equation}
E(r_p)=r_f+\beta_j[E(r_m) - rf] \\
\end{equation}

\begin{equation}
k_E=r_f+\beta_E[E(r_m) - rf] 
\end{equation}

\begin{equation}
k_G=r_f+\beta_G[E(r_m) - rf] 
\end{equation}

\begin{equation}
k_T= k_E\underset{=w_E}{\frac{E}{E+G}} + 
k_G(1-s)\underset{=w_G}{\frac{G}{E+G}}
\end{equation}

\begin{equation}
k_T= k_Ew_E + k_G(1-s)w_G
\end{equation}






