---
title: ""
output: github_document
---

```{r, eval=T, echo=F}
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/forelesningsnotater/timeplan.R'))
```

## Forelesning #1: [`r tema[1]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/1_introduksjon_og_overblikk.pdf)
## Forelesning #2: [`r tema[2]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/2_relevant_risiko_2_obj.pdf)
## Forelesning #3: [`r tema[3]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/3_relevant_risiko_3_N_obj.pdf)
## Forelesning #4: [`r tema[4]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/4_Effisiens.pdf)
## Forelesning #5: [`r tema[5]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/5_Kapitalverdimodellen.pdf)
## Forelesning #6: [`r tema[6]`](https://github.com/joernih/SFB30820Finansteori/blob/main/inst/forelesningsnotater/6_Langsiktige_finansieringsformer.pdf)
## Forelesning #7:  `r tema[8]`()
## Forelesning #8:  `r tema[9]`()
## Forelesning #9:  `r tema[10]`()
## Forelesning #10: `r tema[11]`
## Forelesning #11: `r tema[12]`
## Forelesning #12: `r tema[13]`

```{r, echo=F, eval=T}
knitr::knit_exit()
```

## Forelesning #4: [`r tema[4]`]()
## Forelesning #5: [`r tema[5]`]()
## Forelesning #6: [`r tema[6]`]()
## Forelesning #7: [`r tema[7]`]()
## Forelesning #8: [`r tema[9]`]()
## Forelesning #9: [`r tema[10]`]()
## Forelesning #10: [`r tema[11]`]()
## Forelesning #11: [`r tema[12]`]()
## Forelesning #12: [`r tema[13]`]()
